Results

### 2019-09-18 analysis/03_analysis.Rmd
errors encountered loading packages

```{r load-packages, warning=FALSE, message=FALSE}
library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(bayesm)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

@@

@@

```{r plot-marginals}
intercept <- 1                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}

>>>>

```{r load-packages, warning=FALSE, message=FALSE}
#install.packages("donorheuristics")
# Error: package ‘donorheuristics’ is not available (for R version 3.6.1)
#install.packages("rstan")
#install.packages("bayesplot")
#install.packages("tidybayes")
#install.packages("bayesm")
#install.packages("ggridges")
#install.packages("ggraph")
#install.packages("ggdag")
#install.packages("here")

library(tidyverse)
library(donorheuristics)
library(rstan)
library(bayesplot)
library(tidybayes)
library(bayesm)
library(ggridges)
library(ggraph)
library(ggdag)
library(here)

@@

# giving me the error: "Error in loadNamespace(name) : there is no package called ‘pander’"

@@

```{r plot-marginals}
intercept <- 0                            # Intercept-only
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 1                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# Plot marginals
if (intercept == 1) {
  draws %>% 
    mutate(
      levels = factor(i, labels = level_labels)
    ) %>%
    ggplot(aes(x = Theta, y = levels)) + 
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Attribute Levels")
}
if (intercept != 1) {
  draws %>% 
    filter(j != 1) %>% 
    mutate(
      levels = factor(i, labels = level_labels),
      covariates = factor(j, labels = covariate_labels)
    ) %>%
    ggplot(aes(x = Theta, y = covariates)) + 
    # what other geoms could we use
    # how to filter to zoom in on a certain part of the graph
    geom_halfeyeh(.width = .95) +
    geom_vline(xintercept = 0, color = "grey") +
    labs(y = "Covariates") +
    facet_wrap(~ levels, ncol = 5)
}
